---
title: "Nomad2018 Predicting Transparent Conductors"
author: "Pranjal Vijay"
date: "January 17, 2018"
output:
  html_document: default
  pdf_document: default
---
##Load the libraries
```{r}
library(caret)
library(ggplot2)
library(dplyr)
library(randomForest)
```
##Load the Data
```{r}
Training_Data<-read.csv("C:/Users/ddddd/Comptitions/Kaggle/Nomad2018 Predicting/train.csv", stringsAsFactors = F)
Test_Data<-read.csv("C:/Users/ddddd/Comptitions/Kaggle/Nomad2018 Predicting/test.csv", stringsAsFactors = F)
```

##Data Exploration

```{r}
names(Training_Data)
```

```{r}
str(Training_Data)
```
```{r}
Training_Data$id <- as.numeric(Training_Data$id )     
Training_Data$spacegroup <-  as.numeric(Training_Data$spacegroup   )      
```
```{r}
str(Training_Data)
```


##Checking the Na values
```{r}
sapply(Training_Data, function(x) {sum(is.na(x))})

```

Here, we can see that there are no any NA value in both datasets.

###Research question:
We have already given a research question by this competition itself.

the prediction of two target properties: the formation energy (which is an indication of the stability of a new material) and the bandgap energy (which is an indication of the potential for transparency over the visible range) to facilitate the discovery of new transparent conductors and allow for advancements in the above-mentioned technologies.

For each id in the test set, you must predict a value for both formation_energy_ev_natom and bandgap_energy_ev. 

```{r}
Training_Data %>% 
  filter( id != "NA", spacegroup != "NA", number_of_total_atoms != "NA", percent_atom_al != "NA", percent_atom_ga != "NA", percent_atom_in != "NA", lattice_vector_1_ang != "NA", lattice_vector_2_ang != "NA", lattice_vector_3_ang != "NA", lattice_angle_alpha_degree != "NA", lattice_angle_beta_degree != "NA", lattice_angle_gamma_degree != "NA", formation_energy_ev_natom != "NA", bandgap_energy_ev != "NA") %>%
  select( id, spacegroup, number_of_total_atoms, percent_atom_al, percent_atom_ga, percent_atom_in   , lattice_vector_1_ang, lattice_vector_2_ang, lattice_vector_3_ang, lattice_angle_alpha_degree, lattice_angle_beta_degree, lattice_angle_gamma_degree, formation_energy_ev_natom,  bandgap_energy_ev ) %>% 
  str()
```

```{r}
Training_Data %>% 
  filter( id != "NA", spacegroup != "NA", number_of_total_atoms != "NA", percent_atom_al != "NA", percent_atom_ga != "NA", percent_atom_in != "NA", lattice_vector_1_ang != "NA", lattice_vector_2_ang != "NA", lattice_vector_3_ang != "NA", lattice_angle_alpha_degree != "NA", lattice_angle_beta_degree != "NA", lattice_angle_gamma_degree != "NA", formation_energy_ev_natom != "NA", bandgap_energy_ev != "NA") %>%
  select( id, spacegroup, number_of_total_atoms, percent_atom_al, percent_atom_ga, percent_atom_in   , lattice_vector_1_ang, lattice_vector_2_ang, lattice_vector_3_ang, lattice_angle_alpha_degree, lattice_angle_beta_degree, lattice_angle_gamma_degree, formation_energy_ev_natom,  bandgap_energy_ev ) %>% 
  group_by(id, spacegroup, number_of_total_atoms, percent_atom_al, percent_atom_ga, percent_atom_in   , lattice_vector_1_ang, lattice_vector_2_ang, lattice_vector_3_ang, lattice_angle_alpha_degree, lattice_angle_beta_degree, lattice_angle_gamma_degree, formation_energy_ev_natom,  bandgap_energy_ev) 
  
  
```



##Scatter plots to see the correlation between variable of x axis and y axis

###Plot for bandgap energy versus id

```{r}
qplot(id, bandgap_energy_ev,data=Training_Data)
```


###Plot for Formation Energy versus id
```{r}
qplot(id, formation_energy_ev_natom,data=Training_Data)
```



##Modelling
This is for prediction of two target properties :the formation energy (which is an indication of the stability of a new material) and the bandgap energy (which is an indication of the potential for transparency over the visible range) 

###model for bandgape energy
```{r}
bandgap_energy_Model = lm(bandgap_energy_ev ~   id+spacegroup+number_of_total_atoms+percent_atom_al +           percent_atom_ga+percent_atom_in+lattice_vector_1_ang+lattice_vector_2_ang +      lattice_vector_3_ang+lattice_angle_alpha_degree + lattice_angle_beta_degree+ lattice_angle_gamma_degree    ,data=Training_Data)
summary(bandgap_energy_Model)
```
```{r}
plot(bandgap_energy_Model)
```



###model for formation energy
```{r}
formation_energy_Model = lm(formation_energy_ev_natom ~   id+spacegroup+number_of_total_atoms+percent_atom_al +           percent_atom_ga+percent_atom_in+lattice_vector_1_ang+lattice_vector_2_ang +      lattice_vector_3_ang+lattice_angle_alpha_degree + lattice_angle_beta_degree+ lattice_angle_gamma_degree    ,data=Training_Data)
summary(formation_energy_Model)

```

```{r}
plot(formation_energy_Model)
```


##Predtions on Test Data
```{r}
formation_pred <- predict(formation_energy_Model, Test_Data)
plot(formation_pred)
```

```{r}
bandgap_pred <- predict(bandgap_energy_Model, Test_Data)
plot(bandgap_pred)
```

## Data for submission
```{r}
Predicted_Outcome <- data.frame(id = 1:600, formation_energy_ev_natom = formation_pred, bandgap_energy_ev = bandgap_pred)
```
```{R}
colnames(Predicted_Outcome) <- c("id","formation_energy_ev_natom","bandgap_energy_ev")
write.csv(Predicted_Outcome,"Predicted_Outcome.csv",row.names = FALSE)
```
 This Prediction helps to avoid costly and inefficient trial-and-error of synthetic methods.
