---
title: "Nomad2018 Predicting Transparent Conductors"
author: "Pranjal Vijay"
date: "January 17, 2018"
output:
  html_document: default
  pdf_document: default
---
##Load the libraries
```{r}
library(caret)
library(ggplot2)
library(dplyr)
library(randomForest)
```
##Load the Data
```{r}
Training_Data<-read.csv("C:/Users/ddddd/Comptitions/Kaggle/Nomad2018 Predicting/train.csv", stringsAsFactors = F)
Test_Data<-read.csv("C:/Users/ddddd/Comptitions/Kaggle/Nomad2018 Predicting/test.csv", stringsAsFactors = F)
```
##Checking the Na values
```{r}
sapply(Training_Data, function(x) {sum(is.na(x))})

```

```{r}
sapply(Test_Data, function(x) {sum(is.na(x))})
```
Here, we can see that there are no any NA value in both datasets.

##Dimensions of both data sets
```{r}
dim(Training_Data)
```
```{r}
dim(Test_Data)
```

##Scatter plots to see the correlation between variable of x axis and y axis

###Plot for bandgap energy versus id

```{r}
qplot(id, bandgap_energy_ev,data=Training_Data)
```


###Plot for Formation Energy versus id
```{r}
qplot(id, formation_energy_ev_natom,data=Training_Data)
```



##Modelling
This is for prediction of two target properties :the formation energy (which is an indication of the stability of a new material) and the bandgap energy (which is an indication of the potential for transparency over the visible range) 

###model for bandgape energy
```{r}
bandgap_energy_Model <- randomForest(
 bandgap_energy_ev ~   id +spacegroup+number_of_total_atoms+percent_atom_al +           percent_atom_ga+percent_atom_in+lattice_vector_1_ang+lattice_vector_2_ang +      lattice_vector_3_ang+lattice_angle_alpha_degree + lattice_angle_beta_degree+ lattice_angle_gamma_degree    ,data=Training_Data,method="rf")
bandgap_energy_Model
```
```{r}
plot(bandgap_energy_Model)
```

###model for formation energy

```{r}
formation_energy_Model <- randomForest(
 formation_energy_ev_natom ~   id +spacegroup+number_of_total_atoms+percent_atom_al +           percent_atom_ga+percent_atom_in+lattice_vector_1_ang+lattice_vector_2_ang +      lattice_vector_3_ang+lattice_angle_alpha_degree + lattice_angle_beta_degree+ lattice_angle_gamma_degree    ,data=Training_Data,method="rf")
formation_energy_Model
```


```{r}
plot(formation_energy_Model)
```


##Predtions on Test Data
```{r}
formation_Prediction <- predict(formation_energy_Model,Test_Data)
```

```{r}
bandgap_Prediction <- predict(bandgap_energy_Model,Test_Data)
```

## Data for submission
```{r}
Predicted_Outcome <- data.frame(id = 1:600, formation_energy_ev_natom = formation_Prediction, bandgap_energy_ev = bandgap_Prediction)
```
```{R}
colnames(Predicted_Outcome) <- c("id","formation_energy_ev_natom","bandgap_energy_ev")
write.csv(Predicted_Outcome,"Predicted_Outcome.csv",row.names = FALSE)
```
 This Prediction helps to avoid costly and inefficient trial-and-error of synthetic methods.
